\documentclass[a4paper,11pt]{article}

\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

\begin{document}
\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{LU ZHUOYI} \\[7.5pt]
\href{mailto:lzhuoyi001@e.ntu.edu.sg}{\raisebox{-0.05\height}\faEnvelope \ lzhuoyi001@e.ntu.edu.sg} \ $|$ \ 
\url{https://lzhuoyi.github.io/Zhuoyi_Lu.github.io}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
Aug 2022 -- Jun 2026 & \textbf{Nanyang Technological University, Singapore} \hfill (CGPA: 4.64/5.00, Top 5\%) \\
& Bachelor of Mechanical Engineering \\
& Robotics and Mechatronics Stream, Minor in Mathematics \\
Jun 2025 -- Aug 2025 & \textbf{Rice University, Houston, Texas, United States of America} \\
& Summer Research Intern @RobotPI Lab under Prof. Kaiyu Hang\\
Sep 2016 -- Jun 2022 & \textbf{Desheng School, Guangdong, China} \\
& International Baccalaureate Diploma (IBDP): 41/45 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERTISE
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming \& Tools} & Python, Anaconda/Conda, MATLAB, C/C++ , Linux Bash \\[3pt]
\textbf{Robotics \& Middleware} & ROS1/2, MuJoCo, Maniskill\\[3pt] 
\textbf{Hardware \& Embedded} & Arduino, SolidWorks, Autodesk Fusion, CAN protocol\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Research EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Research Experience}
\begin{joblong}{Robotics Research Centre (RRC), NTU Singapore}{May 2024 -- Present}
\item Research on Series-Elastic Actuator model of HEBI motor. Designed experiments for motor parameter estimation e.g., Armature (Torque-Current), Velocity Constant (Voltage-Velocity) with PWM and PID control.
\item Built dual planar system consisting of two 2DOF robots and 6DOF arms with HEBI motors. Establish Tele-operation based Impedance control through Forward Kinematics and Jacobian.
\item Research on Motion Planning based on Manipulation Potential under Quasi-Static Assumption. Trajectory/DMP Optimization based on Black-Box Optimization (BBO).
\end{joblong}

\begin{joblong}{Rice University, Houston, Texas, United States of America}{Jun 2025 -- Aug 2025}
\item Develop the codebase (e.g., Keyboard, XBOX joystick and VR Teleoperation Control) for XLeRobot: Fully Autonomous Household Dual-Arm Mobile Robot for \$660 (\url{https://github.com/Vector-Wangel/XLeRobot}). 
\item RGB/Semantic Segmentation based Reinforcement Learning (PPO) via ManiSkill and zero-shot real-world deployment. Developed based on Stones's LeRobot Sim2Real codebase.
\end{joblong}

\begin{joblong}{Delta Electronics, Singapore}{Jan 2025 -- May 2025}
\item Gazebo and Mujoco Simulation of quadruped jumping using virtual spring-damper system in each leg' hip and foot frame. Real World Deployment through Unitree Mujoco and ROS2.
\item Integrate Mujoco with Pinocchio Library for a basic simulation framework in C++ for Manipulation/Locomotion Tasks.
\end{joblong}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{joblong}{Undergraduate Research Program (URECA) under Prof. K Jimmy Hsia}{Jul 2023 -- Jun 2024}
\item Developed a new frontal photopolymerization strategy for functionally-graded materials based on UV attenuation. Published in URECA Papers and Posters.
\end{joblong}

\begin{joblong}{Kaggle Competition in Modeling earthquake richter and impacts }{Aug 2023 -- Dec 2023}
\item Model earthquake damage grades in Nepal using location and construction data from Kaggle Dataset.
\item Data cleaning, one-hot encoding, visualization, Random Forest, Logistic Regression, and KNN applied.
\end{joblong}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Yang, L., Turlapati, S.\,H., \textbf{Lu, Z.}, Lv, C., \& Campolo, D., “A Planning Framework for Stable Robust Multi-Contact Manipulation,” in *Proc. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)*, Hangzhou, China, Oct. 2025.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR
%----------------------------------------------------------------------------------------
\section{Extracurricular Activities}
\begin{joblong}{Xinyuan Charity Center, Guangdong, China}{Aug 2020 -- Aug 2021}
\item Organized drawing lessons for autistic children to help them adapt to school and build social relationships.
\end{joblong}

\begin{joblong}{Residential Hall Garden Leader, NTU Singapore}{Aug 2023 -- Present}
\item Led weekly gardening activities, including seed germination, watering, and tool maintenance.
\end{joblong}

%----------------------------------------------------------------------------------------
%	HONORS
%----------------------------------------------------------------------------------------
\section{Honors and Awards}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
\item Dean’s List Certificate AY2023/24 (Top 5\%), Mechanical Engineering, NTU Singapore
\item Dean’s List Certificate AY2024/25 (Top 5\%), Mechanical Engineering, NTU Singapore
\item URECA Undergraduate Research Program 2023/2024 Certificate
\end{itemize}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
